An IFS study of Low-powered Radio Galaxies

### 2019-11-10 paper.tex
Further corrections
 On branch master
 Changes to be committed:
	modified:   paper.tex

In reality, the field of view does not always contain
$1$~$R_\text{e}$. When this is the case, we follow the method of
\citet{Emsellem2007}, where $R_\text{m}$ is redefined as
$R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, where $A_\text{s}$ is the
area of the {\bf (Largest? Clarify.)} ellipse contained within the
field of view. {\bf (I do not understand the meaning of the following
  sentence in {\it italics}. Rephrase/explain better. Perhaps even
  simply remove? What are $R_\text{max}$ and $A_\text{ellipse}$?!)}
{\it For a given galaxy, we fit ellipses as described above, up to
  $R_\text{m}=R_\text{max}$, where $A_\text{s}$ reaches a maximum
  difference of 15\% with respect to the area of the fitted ellipse,
  $A_\text{ellipse}$}. The value $\epsilon_\text{e}$, the ellipticity
at $1$~$R_\text{e}$ or $R_\text{max}$, whichever is smallest, is given
in Column~3 of Table~\ref{tab:classify}.

@@

The kinematic position angle, $PA_\text{kin}$, is defined as the angle
of the axis perpendicular to the apparent angular momentum vector,
measured westward from North. {\bf (Are you sure this is westward and
  not eastward? Position angles are usually defined from North to
  East, the latter of course usually being to the left in astronomical
  images. Check and correct if need be.)} A global value of
$PA_\text{kin}$ is calculated using the \textsc{python} routine
\textsc{fit\_kinematic\_pa}\footnotemark[1], that finds
$PA_\text{kin}$ of the symmetrised mean velocity map, as described in
Appendix~C of \citet{Krajnovic2006}.
% This routine finds a symmetric (about $PA_\text{kin}$) velocity
% field, by replacing the mean velocity, $V$, in each bin with
% \begin{equation}
% V'(x, y) = \frac{V(x,y) + V(x, -y) - V(-x,y) - V(-x,-y))}{4}~,
% \end{equation}
% where $x$ and $y$ are the centroid coordinates of a given bin, with
% the origin at the centre of the galaxy and the x axis aligned along
% $PA_\text{kin}$. Linear interpolation is used where necessary.

Column~4 in Table~\ref{tab:classify} lists the misalignment angle
between the photometric and stellar kinematic position angles,
$\Gamma_\text{kin}\equiv\arcsin(\sin[PA_\text{phot}-PA_\text{kin}])$.
{\bf (Why is that different from simply
  $\Gamma_\text{kin}\equiv PA_\text{phot}-PA_\text{kin}$? Correct if
  need be.)} {\bf (At which radius/ellipse semi-major axis is
  $PA_\text{phot}$ taken/measured? Specify.)}

@@

We also make use of the Atlas$^\text{3D}$ specific angular momentum
parameter, $\lambda_\text{R}$ \citep{Emsellem2007}, evaluated at
$1$~$R_\text{e}$, where
\begin{equation}
  \lambda_\mathrm{R_e}\equiv\frac{\sum_{i=1}^{N}\,F_iR_i|V_i|}{\sum_{i=1}^{N}\,F_iR_i\sqrt{V_i^2+\sigma_i^2}}~,
\end{equation}
{\bf (Is $R_i$ really measured from the centre as stated, or rather
  with respect to the kinematic minor axis/rotation axis?
  State/explain if the latter.)} where $F_i$ is the flux of the
$i^\text{th}$ bin, $R_i$ its distance from the centre, $V_i$ its mean
stellar velocity and $\sigma_i$ its stellar velocity dispersion. The
sum is computed over all $N$ bins within $1$~$R_\text{e}$ of the
centre of the galaxy. {\bf (What do you do if the field of view does
  not reach $1$~$R_\text{e}$? Specify/discuss (as for
  $\epsilon_\text{e}$).)}

>>>>

In reality, the field of view does not always \added{fully} contain 
\added{a given fitted ellipse} \removed{$1$~$R_\text{e}$}. When this 
is the case, we follow the method of \citet{Emsellem2007}, where 
$R_\text{m}$ is redefined as $R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, 
where $A_\text{s}$ is the area \added{contained within 
the field of view} of the {\bf (Largest? Clarify.)} 
\added{given} ellipse \removed{contained within 
the field of view}. {\bf (I do not understand the meaning of the 
following sentence in {\it italics}. Rephrase/explain better. 
Perhaps even simply remove? What are $R_\text{max}$ and 
$A_\text{ellipse}$?!)} {\it For a given galaxy, we fit ellipses 
as described above, up to $R_\text{m}=R_\text{max}$, where 
\added{$R_\text{max}$ is defined such that  
$\frac{A_\text{s}(R_\text{max})}{A_\text{ellipse}(R_\text{max})} 
\equiv 0.15$ or $R_\text{max} = R_\text{e}$, which ever is smallest.} 
\removed{$A_\text{s}$ reaches a maximum difference of 15\% with 
respect to the area of the fitted ellipse, $A_\text{ellipse}$.}} The 
value $\epsilon_\text{e}$, the ellipticity \added{of this largest 
fitted ellipse} \removed{at $1$~$R_\text{e}$ or $R_\text{max}$, 
whichever is smallest}, is given in Column~3 of 
Table~\ref{tab:classify}.

@@

The kinematic position angle, $PA_\text{kin}$, is defined as the angle
of the axis perpendicular to the apparent angular momentum vector,
measured \added{eastward} \removed{westward} from North. {\bf (Are you sure this is westward and
  not eastward? Position angles are usually defined from North to
  East, the latter of course usually being to the left in astronomical
  images. Check and correct if need be.)} A global value of
$PA_\text{kin}$ is calculated using the \textsc{python} routine
\textsc{fit\_kinematic\_pa}\footnotemark[1], that finds
$PA_\text{kin}$ of the symmetrised mean velocity map, as described in
Appendix~C of \citet{Krajnovic2006}.
% This routine finds a symmetric (about $PA_\text{kin}$) velocity
% field, by replacing the mean velocity, $V$, in each bin with
% \begin{equation}
% V'(x, y) = \frac{V(x,y) + V(x, -y) - V(-x,y) - V(-x,-y))}{4}~,
% \end{equation}
% where $x$ and $y$ are the centroid coordinates of a given bin, with
% the origin at the centre of the galaxy and the x axis aligned along
% $PA_\text{kin}$. Linear interpolation is used where necessary.

Column~4 in Table~\ref{tab:classify} lists the misalignment angle
between the photometric and stellar kinematic position angles,
$\Gamma_\text{kin}\equiv\arcsin(\sin[PA_\text{phot}-PA_\text{kin}])$
{\bf (Why is that different from simply
  $\Gamma_\text{kin}\equiv PA_\text{phot}-PA_\text{kin}$? Correct if
  need be.)} {\bf (At which radius/ellipse semi-major axis is
  $PA_\text{phot}$ taken/measured? Specify.)} \added{, where$PA_\text{phot}$ is measured at $R_\text{max}$.}

@@

We also make use of the Atlas$^\text{3D}$ specific angular momentum
parameter, $\lambda_\text{R}$ \citep{Emsellem2007}, evaluated at
$1$~$R_\text{e}$, where
\begin{equation}
  \lambda_\mathrm{R_e}\equiv\frac{\sum_{i=1}^{N}\,F_iR_i|V_i|}{\sum_{i=1}^{N}\,F_iR_i\sqrt{V_i^2+\sigma_i^2}}~,
\end{equation}
{\bf (Is $R_i$ really measured from the centre as stated, or rather
  with respect to the kinematic minor axis/rotation axis?
  State/explain if the latter. JW: $R_i$ is from the center - see Eq6 in \citep{Emsellem2007})} where $F_i$ is the flux of the
$i^\text{th}$ bin, $R_i$ its distance from the centre, $V_i$ its mean
stellar velocity and $\sigma_i$ its stellar velocity dispersion. The
sum is computed over all $N$ bins within \removed{$1$~$R_\text{e}$} \added{$1$~$R_\text{max}$} of the
centre of the galaxy. {\bf (What do you do if the field of view does
  not reach $1$~$R_\text{e}$? Specify/discuss (as for
  $\epsilon_\text{e}$).)}
